EGGs are adhesive!

### 2025-07-28 jlamp/jlamp.tex
minima

\author[1]{Roberto Biondo}
\ead{r.biondo@studenti.unipi.it}

\author[1]{Davide Castelnovo\corref{cor1}%
}
\ead{castelnovod@gmail.com}
%{https://orcid.org/0000-0002-5926-5615}{}

\author[1]{Fabio Gadducci}
\ead{fabio.gadducci@unipi.it}
%{https://orcid.org/0000-0003-0690-3051}{}

@@

\affiliation[1]{organization = {Department of Computer Science, University of Pisa},
	addressline = {Largo B. Pontecorvo, 3},
	postcode = {56127},
	city = {Pisa}, 
	country = {Italy}}

>>>>

\author{Roberto Biondo}
\ead{r.biondo@studenti.unipi.it}

\author{Davide Castelnovo\corref{cor1}%
}
\ead{castelnovod@gmail.com}
%{https://orcid.org/0000-0002-5926-5615}{}

\author{Fabio Gadducci}
\ead{fabio.gadducci@unipi.it}
%{https://orcid.org/0000-0003-0690-3051}{}

@@

\affiliation{organization = {Department of Computer Science, University of Pisa},
	city = {Pisa}, 
	country = {Italy}}

\fntext[miur]{Research partially supported by the Italian MUR project PRIN
20228KXFN2 ``STENDHAL''.}
